Dynamics of thin liquid film flows studied with the lattice Boltzmann method

### 2022-12-06 chapters/Introduction.tex
jens_comments_work

Since the 19$^{\text{th}}$ century the theory of lubrication had gain much attention and got extended to account for more complex problems.
Over time it became it clear that problems such as wetting and capillarity can be studied within this framework~\cite{RevModPhys.57.827, RevModPhys.69.931, RevModPhys.81.1131}.
To this end the term thin film equation was introduced, which is nothing more than the functional form that the lubrication approximation yields. 
Wetting for example does strongly depend on the intermolecular forces. 
The DLVO potential made it possible to account for these forces~\cite{derjaguin1941acta, verwey1947theory}. 
DLVO is an acronym from the name of the four scientists Derjaguin, Landau, Verwey and Overbeek who developed this theory. 
Initially this potential was used to understand the stability of colloidal suspensions, however for thin film theory it offers a quantification for the disjoining pressure~\cite{RevModPhys.69.931, Peschka9275, moulton_lega_2013, PhysRevE.63.011208}.
Pierre-Gilles de Gennes, who was awarded with the Nobel Prize in physics in 1991 for his work on soft matter physics and his students were ones of the first who understood that ``\textit{dirty}'' soft matter physics can help in understanding thin film problems~\cite{RevModPhys.57.827,doi:10.1021/la0116342,de2013capillarity}.

>>>>

Since the 19$^{\text{th}}$ century the theory of lubrication had gain much attention and got extended to account for more complex problems.
Over time it became it clear that problems such as wetting and capillarity can be studied within this framework~\cite{RevModPhys.57.827, RevModPhys.69.931, RevModPhys.81.1131}.
To this end the term thin film equation was introduced, which is nothing more than the functional form that the lubrication approximation yields. 
Wetting for example does strongly depend on the intermolecular forces. 
The DLVO potential made it possible to account for these forces~\cite{derjaguin1941acta, verwey1947theory}. 
DLVO is an acronym from the name of the four scientists Derjaguin, Landau, Verwey and Overbeek who developed this theory. 
Initially this potential was used to understand the stability of colloidal suspensions, however for thin film theory it offers a quantification for the disjoining pressure~\cite{RevModPhys.69.931, Peschka9275, moulton_lega_2013, PhysRevE.63.011208}.
Pierre-Gilles de Gennes, who was awarded with the Nobel Prize in physics in 1991 for his work on soft matter physics and his students were ones of the first who understood that ``\textit{dirty}'' soft matter physics can help in understanding thin film problems~\cite{RevModPhys.57.827,doi:10.1021/la0116342,de2003capillarity}.

### 2022-12-06 chapters/Paper_four.tex
jens_comments_work

\textit{\small{This chapter has been submitted as a regular contribution to the Journal of open source software. The review process is performed under the issue number \href{https://github.com/openjournals/joss-reviews/issues/3728}{3728}}}

@@

Lattice Boltzmann solvers offer another category to approximate the Navier-Stokes equation.
Starting point of this method is not the Navier-Stokes equation but the Boltzmann equation.
Using the Chapman-Enskog expansion~\cite{Chapman, Enskog}, it can be shown that the resulting system of equations recovers to the Navier-Stokes equation.
The method is straightforward to implement and several small to large projects can be found with OSI-approved license. 
To name just a few examples: \href{https://walberla.net/doxygen/index.html}{\textbf{waLBerla}}, \href{https://www.openlb.net/}{\textbf{openLB}} or some smaller project \href{https://gitlab.com/unigehpfs/stlbm}{\textbf{STLBM}}.

@@

>>>>

\textit{\small{This chapter has been published and can be found as: Zitz et al., (2022). Swalbe.jl: A lattice Boltzmann solver for thin film hydrodynamics. Journal of Open Source Software, 7(77), 4312}}

@@

Lattice Boltzmann solvers offer another category to approximate the Navier-Stokes equation.
Starting point of this method is not the Navier-Stokes equation but the Boltzmann equation.
Using the Chapman-Enskog expansion~\cite{Chapman, Enskog}, it can be shown that the resulting system of equations recovers to the Navier-Stokes equation.
The method is straightforward to implement and several small to large projects can be found with OSI-approved license. 
To name just a few examples: \href{https://walberla.net/doxygen/index.html}{\textbf{waLBerla}}, \href{https://www.openlb.net/}{\textbf{openLB}} or some smaller project \href{https://gitlab.com/unigehpfs/stlbm}{\textbf{STLBM}}, \href{https://github.com/FrancescaPelusi/TLBfind}{\textbf{TLBfind}} (explicitly written for GPU use).

@@

\section{Author Contribution Statement}

The authors confirm contribution to the paper as follows: S. Z. wrote the code, performed the simulations and set up the package. 
M. Z. contributed to the  integration as well as the documentation. 
A. S. derived the mathematical approximations on which the packages is based on and J. H. served in an advisory role in the design and the execution of the research.
